 \documentclass[margin,line,pifont,palatino,courier]{res}
%\usepackage{amsfont}
%\usepackage{pifont}
%\usepackage[latin1] { inputenc}
\usepackage{amssymb}







\begin{document}
\section{Publications}
$1) ${\rm{F. IANDOLI, R. Scandone}},  \textit{Dispersive estimates for Schr\"odinger operators with point interactions in $\mathbb{R}^3$,}  {\textbf {Advances in Quantum Mechanics: Contemporary Trends and Open Problems}}, A. Michelangeli and G. Dell'Antonio, eds., Springer INdAM Series, vol. 18, Springer International Publishing, (2017).\vspace{0.1cm}\\
$2) ${\rm{R. Feola, F. IANDOLI}},  \textit{Local well-posedness for quasi-linear NLS with large Cauchy data on the circle,}  \textbf{Annales de l'Institut Henri Poincar\'e (C) Non Linear Analysis}, (1) Vol 36: 119-164, (2019).\vspace{0.1cm}\\
$3) ${\rm{R. Feola, F. IANDOLI}}, \textit{Long time existence for fully nonlinear NLS with small Cauchy data on the circle},   \textbf{Ann. Sc Norm.  Pisa Cl. Sci.} (5), Vol XXII, 109-182, (2021).\vspace{0.1cm}\\
$4) ${\rm{J., Bernier, R. Feola, B. Gr\'ebert, F.IANDOLI}}, \textit{Long-time existence for semi-linear beam equations on irrational tori},  \textbf{J. Dyn. Diff. Equat.} (3), Vol 33, 1363-1398, (2021). \vspace{0.1cm}\\
$5) ${\rm{R. Feola, F. IANDOLI}}, \textit{A non-linear Egorov theorem and Poincar\'e-Birkhoff normal forms for quasi-linear pdes on the circle}, preprint: arxiv.org/abs/2002.12448, (2020).\vspace{0.1cm}\\
$6) ${\rm{R. Feola, F. IANDOLI}}, \textit{Local well-posedness for the quasi-linear Hamiltonian Schr\"odinger equation on tori}, preprint: arxiv.org/abs/2003.04815, (2020). (\textbf{Accepted on Journal de Math\'ematiques pures et appliqu\'ees})\vspace{0.1cm}\\
$7) ${\rm{R. Feola, B. Gr\'ebert, F.IANDOLI}}, \textit{Long time solutions for quasi-linear Hamiltonian perturbations of Schr\"odinger and Klein-Gordon equations on tori}, preprint: arxiv.org/\\abs/2009.07553, (2020). \vspace{0.1cm}\\
$8) ${\rm{R. Feola, F. IANDOLI, F. Murgante}}, \textit{Long-time stability of the quantum hydrodynamical system on irrational tori}, \textbf{Math. in Engineering}, (3), Vol 4, 1-24, (2022).\vspace{0.1cm}\\
\end{document}
